Sustainable Indicators

### 2021-01-19 01-Sustainable-indicators.Rmd
sustainable indicator PPS&Q V1.0.1

Therefore, contextualizing the concptual framework to the DRAM context, the main research question is for this project are:

@@

2.*What are the the 'pertinent' qualitative and quantitative indicators to evaluate the local distributed recycling network in terms of revelance of quality and feasibility to obtain appropriate data with local stakeholders?*

One element to highlight the impact that third-spaces as innovations labs, fablabs and/or makerspace can play an role as agents of change in the development of this recycling practicesl [@Roux-Marchand2020]

>>>>

Therefore, contextualizing thi sustainable concptual framework to the DRAM context, the main research question is for this project are:

@@

2.*What are the 'pertinent' qualitative and quantitative indicators to evaluate the local distributed recycling network in terms of revelance of quality and feasibility to obtain appropriate data with local stakeholders?*

One element to highlight is the impact that third-spaces such as innovations labs, fablabs and/or makerspace can play, having a role of agents of change in the development of this recycling practices [@Roux-Marchand2020].
